Who needs privacy? Exploring the relations between need for privacy and personality

### 2023-03-07 analyses.RmD
- last updates before sending to Miriam
- updates before submission

---
title: "Who Needs Privacy? Exploring the relationship between personality and need for privacy"
subtitle: "Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
  # pdf_document:
  #   toc: TRUE
---

@@

- At this point, we haven't yet collected data. 
- The results below use simulated data. 
- The data are random and don't make sense, but help to illustrate the overall approach and planned analyses.
- We'll later conduct further analyses not yet reported here, for example model-alterations given misfit.

@@

 - I feel reasonably satisfied with myself overall.
 - I think that most people like some aspects of my personality.
 - I feel that I am an unpopular person.
 - Even in an emergency I wouldn't feel like panicking.

>>>>

---
title: "Who needs privacy? Exploring the relations between need for privacy and personality"
subtitle: "Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
---

@@

- At this point, we haven't yet collected data. 
- The results below use simulated data. 
- The data are random and don't make sense, but help to illustrate the overall approach and planned analyses.
- We'll later conduct further analyses not yet reported here, for example model-alterations given misfit or imputation of missing data.

@@

 - I feel reasonably satisfied with myself overall.
 - I think that most people like some aspects of my personality.
 - I feel that I am an unpopular person.
 - I sometimes feel that I am a worthless person.
